How Slow do my Transient Typechecks Go?

### 2019-08-14 paper.tex
Fix my country/email, added orcid
Signed-off-by: Stefan Marr <git@stefan-marr.de>
Added collab.sty to be able to comment conveniently
Signed-off-by: Stefan Marr <git@stefan-marr.de>
Edit and comment abstract
Signed-off-by: Stefan Marr <git@stefan-marr.de>

@@

\author{Stefan Marr}
\affiliation{
  \department{School of Computing} % \department is recommended
  \institution{University of Kent}
  \country{s.marr@kent.ac.uk}
}
\email{mwh@ecs.vuw.ac.nz} % \email is recommended

@@

\begin{abstract}
Just-in-time compilation and optimisation in virtual machines can
eliminate much of the overhead of transient typechecks.  Unfortunately
the improvement is not uniform: while most typechecks can be optimised
away, some typechecks will will significantly decrease a program's
performance.  In this paper we investigate how benchmark results can be
indicate which typechecks cause the most problems. Programmers could
use these techniques to optimise their programs by removing
typechecks, and VM engineers to identify opportunities for further
optimisations.   
\end{abstract}

>>>>

\usepackage{collab}

\collabAuthor{rr}{green!60!black}{Richard}
\collabAuthor{sm}{red}{Stefan}
\collabAuthor{kjx}{orange}{James}
\collabAuthor{mwh}{purple}{Michael}

@@

\author{Stefan Marr}
\orcid{0000-0001-9059-5180}
\affiliation{
  \department{School of Computing} % \department is recommended
  \institution{University of Kent}
  \country{United Kingdom}
}
\email{s.marr@kent.ac.uk} % \email is recommended

@@

\begin{abstract}
Just-in-time compilation and optimisation in virtual machines can
eliminate much of the overhead of transient typechecks.  Unfortunately
the improvement is not uniform: while most typechecks can be optimised
away, some typechecks will significantly decrease a program's
performance.

In this paper we investigate how benchmark results can be
used to identify which typechecks cause performance issues. Programmers could
use these techniques to optimise their programs by removing
typechecks, and VM engineers to identify opportunities for further
optimisations.

\sm{this is much to brief for me.
Transient typechecks is a very specific thing.
I believe, VM people need more context here.
It's a form of gradual typing, which requires comparably simple checks
at run time to check type violations.
Then, how do we investigate the issues? we should give a hint what the solution is. otherwise, the sentence in using these techniques doesn't make sense to me, because we didn't say anything about them.}
\end{abstract}
